Asteroid shape reconstruction

### 2018-03-23 abstract.tex
Adding more to intro

\begin{itemize}
    \item Spacecraft missions around asteroid require long periods of mapping
        \begin{itemize}
            \item Several months/years are spent in a quiescent state devoted solely to mapping the surface
            \item Depending on the mission this time spent mapping is unnecessary and resource limiting - such as impact mitigation misions
            \item The main goal of this mapping process is to generate an accurate shape model of the asteroid and measure the surface features.
            \item The current methods rely on sending all data to the ground in order to compute the shape. 
            \item Furthermore this limits the abiilty  of teh spacecraft to operate without  reliable Earth communications and support
        \end{itemize}
    \item The surface shape is necessary in order to allow the spacecraft to operate near the surface of the a steroid
        \begin{itemize}
            \item The polyhedron potential model is a function of the shape and highly dependent on an accurate shape model.
            \item It is not possible to accurately determine the shape of the asteroid from ground based measurements.
                Due to the limitations of optical and radar measurements the typical best shape approximation prior to arrival is a coarse ellispoid shape CITE a paper.
            \item The shape is
        \end{itemize}
\end{itemize}

>>>>

\begin{enumerate}
    \item Spacecraft missions around asteroid require long periods of mapping
        \begin{itemize}
            \item Several months/years are spent in a quiescent state devoted solely to mapping the surface
            \item Depending on the mission this time spent mapping is unnecessary and resource limiting - such as impact mitigation misions
            \item The main goal of this mapping process is to generate an accurate shape model of the asteroid and measure the surface features.
            \item The current methods rely on sending all data to the ground in order to compute the shape. 
            \item Furthermore this limits the abiilty  of teh spacecraft to operate without  reliable Earth communications and support
        \end{itemize}
    \item The surface shape is necessary in order to allow the spacecraft to operate near the surface of the a steroid
        \begin{itemize}
            \item The polyhedron potential model is a function of the shape and highly dependent on an accurate shape model.
            \item It is not possible to accurately determine the shape of the asteroid from ground based measurements.
                Due to the limitations of optical and radar measurements the typical best shape approximation prior to arrival is a coarse ellispoid shape CITE a paper.
            \item An accurate shape model is critical for not only the gravitational model but also to enable accurate landing operations.
                An accurate model of the surface is required for the gravity model, surface landing operations, and obstacle avoidance.
        \end{itemize}
    \item Due to the previous issues it is critical to be able to generate the shape of the asteroid surface accurately and quickly.
        \begin{itemize}
            \item This work develops a method to efficiently determine the shape of the an asteroid given LIDAR range measurements of the surface.
            \item The shape is updated in near real time (QUANTIFY THIS IN SOME MEANINGFUL FASHION) to  enable:
                \begin{itemize}
                    \item Updated gravity/dynamic model 
                    \item Utilize this updated dynamic model in the spacecraft controller
                    \item Allow for simulataenous shape reconstruction and spacecraft control
                \end{itemize}
            \item This alleviates teh need for a long term mapping campaign
        \end{itemize}
\end{enumerate}
